Create Nomogram

### 2024-01-19 Code/05_FitModels.Rmd
Final edits

form.BS.Rec.5 <- S.Rec.5.training ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.Rec.5 <- Hmisc::fit.mult.impute(form.BS.Rec.5,cph,
                                        xtrans=imputed.training.data,
                                        data=training.data.to.be.imputed,
                                        n.impute=m, pr=FALSE,fit.reps=TRUE,
                                        fitargs=list(y=TRUE,x=TRUE,se.fit=TRUE))
# backward selection
# round(stats::anova(f.mi.BS.Rec.5)[order(stats::anova(f.mi.BS.Rec.5)[, "P"]),], 3)
summary(f.mi.BS.Rec.5, Breslow=exp(c.Breslow))
coef(f.mi.BS.Rec.5)
stats::anova(f.mi.BS.Rec.5)
```

@@

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", 
            "form.full.Rec.5", "form.BS.Rec.5", "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.RData")
save(list=c("dd.validation", "validation.data.to.be.imputed", "m", 
            "imputed.validation.data", "last.imputed.validation.data.set", "horizon", 
            "S.Rec.5.validation", "S.MSM.5.validation", "f.mi.BS.Rec.5"),
     file=paste0("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata"), compress=TRUE)
```

@@

# c-index
p.MSM.5.redev<- matrix(NA, nrow(training.data.to.be.imputed), m)
f.MSM.basehaz <- survival::basehaz(cph(form.full.MSM.5.redev, 
                             data=mice::complete(imputed.training.data, 1), 
                             se.fit=TRUE, x=TRUE, y=TRUE))
h0.MSM.redev <- f.MSM.basehaz$hazard[f.MSM.basehaz$time==max(f.MSM.basehaz$time[f.MSM.basehaz$time<=horizon])]
for (i in 1:m){
  lp.val.i <- predict(f.mi.full.MSM.5.redev,
                      newdata=mice::complete(imputed.training.data, i),
                      type="lp")
  p.MSM.5.redev[, i] <- 1-exp(-h0.MSM.redev*exp(lp.val.i))
}
PredictionTools::val.surv.mi(p.MSM.5.redev, S.MSM.5.training, g=5,
                             main="All patients", time=NULL, lim=c(0, 1),
                             dist=TRUE)
```

>>>>

form.BS.Rec.5 <- S.Rec.5.training ~
  SNstatus +
  Age.SN +
  Ulceration +
  Loc_CAT +
  I(log(Breslow)-c.Breslow) +
  log(Rdamcrit) +
  SNstatus:I(log(Breslow)-c.Breslow)
f.mi.BS.Rec.5 <- Hmisc::fit.mult.impute(form.BS.Rec.5,cph,
                                        xtrans=imputed.training.data,
                                        data=training.data.to.be.imputed,
                                        n.impute=m, pr=FALSE,fit.reps=TRUE,
                                        fitargs=list(y=TRUE,x=TRUE,se.fit=TRUE))

# check Cox Proportional Hazards Assumption
PH.assumption <- survival::cox.zph(f.mi.BS.Rec.5)

# backward selection
# round(stats::anova(f.mi.BS.Rec.5)[order(stats::anova(f.mi.BS.Rec.5)[, "P"]),], 3)
summary(f.mi.BS.Rec.5, Breslow=exp(c.Breslow))
coef(f.mi.BS.Rec.5)
stats::anova(f.mi.BS.Rec.5)
```

@@

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", 
            "form.full.Rec.5", "form.BS.Rec.5", "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.RData")
save(list=c("dd.validation", "validation.data.to.be.imputed", "m", 
            "imputed.validation.data", "last.imputed.validation.data.set", "horizon", 
            "S.Rec.validation", "S.MSM.validation", 
            "S.Rec.5.validation", "S.MSM.5.validation", "f.mi.BS.Rec.5"),
     file=paste0("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata"), compress=TRUE)
```

@@

# c-index
p.MSM.5.redev<- matrix(NA, nrow(training.data.to.be.imputed), m)
f.MSM.basehaz <- survival::basehaz(cph(form.full.MSM.5.redev, 
                             data=mice::complete(imputed.training.data, 1), 
                             se.fit=TRUE, x=TRUE, y=TRUE))
h0.MSM.redev <- f.MSM.basehaz$hazard[f.MSM.basehaz$time==max(f.MSM.basehaz$time[f.MSM.basehaz$time<=horizon])]
for (i in 1:m){
  lp.val.i <- predict(f.mi.full.MSM.5.redev,
                      newdata=mice::complete(imputed.training.data, i),
                      type="lp")
  p.MSM.5.redev[, i] <- 1-exp(-h0.MSM.redev*exp(lp.val.i))
}
PredictionTools::val.surv.mi(p.MSM.5.redev, S.MSM.training, g=5,
                             main="All patients", time=5, lim=c(0, 1),
                             dist=TRUE)
```

### 2024-01-19 Code/06_CreateTablesandPlots.Rmd
Final edits

# Add C-index to model for Recurrence and MSM refit Table
```{r, eval=TRUE}
for (model in list("Rec.5", "MSM.5.refit")){
  if (model == "Rec.5"){
    # plot predict
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Rec.png"))
    plot.predict <- plot(Predict(f.mi.full.Rec.5))
    show(plot.predict)
    grDevices::dev.off()

    # plot predict Breslow
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Breslow.Rec.png"))
    plot.Breslow <- plot(Predict(f.mi.full.Rec.5, Breslow=0:20, SNstatus), ~ Breslow, groups="SNstatus",
                         adj.subtitle=FALSE, lwd=2, labels=FALSE,
                         par.settings=list(superpose.line=list(lty=c(1, 2), 
                                                               col=c("red", "blue"))),
                         key=list(cex=.8,corner = c(0.1, .9),
                                  lines=list(col=c("red","blue"), 
                                             lty=c(1,2), lwd=2),
                                  text=list(c("Negative","Positive"))))
    show(plot.Breslow)
    grDevices::dev.off()
  }

@@

    # load outcome
    if (model=="Rec.5"){
      S <- S.Rec.5.training
    }
    else if (model=="MSM.5.refit"){
      S <- S.MSM.5.training
    }

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/all.centers.", model, ".", type, ".png"))
    out <- PredictionTools::val.surv.mi(p,S,g=5,main="All centers",
                                        time=NULL,lim=c(0,1),dist=TRUE)
    grDevices::dev.off()

    final.full.table <- eval(parse(text=paste0("final.", type, ".table.", model)))
    final.full.table["C-index", "HR"] <- sprintf("%.2f", out$cindex-optimism)
    final.full.table["C-index", "CI"] <- paste0("[", sprintf("%.2f", out$cindex.lower-optimism),
                                                   "; ", sprintf("%.2f", out$cindex.upper-optimism), "]")

@@

# Add the C-index for calibrated MSM model to Table for recurrence
```{r, eval=TRUE}
for (type in c("full", "BS")){
  f.mi <- eval(parse(text=paste0("f.mi.", type, ".Rec.5")))
  cindex.MSM.cal <- rep(0, m)
  cindex.se.MSM.cal <- rep(0, m)
  for (i in 1:m){
    rc <- Hmisc::rcorr.cens(-predict(f.mi,
                                     newdata=mice::complete(imputed.training.data,i), type="lp"), 
                            S.MSM.5.training)
    cindex.MSM.cal[i] <- rc["C Index"]
    cindex.se.MSM.cal[i] <- rc["S.D."]/2
  }
  cindex.mi.MSM.cal <- Rubin.combine(cindex.MSM.cal, cindex.se.MSM.cal)

  final.full.table <- eval(parse(text=paste0("final.", type, ".table.Rec.5")))
  final.full.table["C-index MSM", "HR"] <- sprintf("%.2f", cindex.mi.MSM.cal$est-optimism)
  final.full.table["C-index MSM", "CI"] <- paste0("[", sprintf("%.2f", cindex.mi.MSM.cal$est+qnorm(.025)*cindex.mi.MSM.cal$se-optimism),
                                                 "; ", sprintf("%.2f", cindex.mi.MSM.cal$est+qnorm(.975)*cindex.mi.MSM.cal$se-optimism), "]")

@@

# set rownames
final.full.table.Rec.5 <- as.data.frame(final.full.table.Rec.5)
row.names(final.full.table.Rec.5) <- c("Positive SN status", "Male",
                                    "Age iqr", "Ulceration", "Location",
                                    "Arm", "Leg", "Trunk", "Head and neck",
                                    "Histology", "SSM", "NM", "ALM", "Other",
                                    "Breslow iqr", "Multiple fields", 
                                    "Total number of negative nodes",
                                    "Total number of positive nodes",
                                    "SN tumour burden iqr", 
                                    "Location metastasis in lymph node",
                                    "Subcap", "Combined", "Parenchymal",
                                    "Multifocal", "Extensive",
                                    rownames(final.full.table.Rec.5)[(nrow(final.full.table.Rec.5)-1):nrow(final.full.table.Rec.5)])
final.full.table.MSM.5.refit <- as.data.frame(final.full.table.MSM.5.refit)
row.names(final.full.table.MSM.5.refit) <- c("Positive SN status", "Male",
                                          "Age", "Ulceration", "Location",
                                          "Arm", "Leg", "Trunk", "Head and neck",
                                          "Histology", "SSM", "NM", "ALM", "Other",
                                          "Breslow", "Multiple fields", 
                                          "Total number of negative nodes",
                                          "Total number of positive nodes",
                                          "SN tumour burden", 
                                          "Location metastasis in lymph node",
                                          "Subcap", "Combined", "Parenchymal",
                                          "Multifocal", "Extensive",
                                          row.names(final.full.table.MSM.5.refit)[nrow(final.full.table.MSM.5.refit)])
final.BS.table.Rec.5 <- as.data.frame(final.BS.table.Rec.5)
row.names(final.BS.table.Rec.5) <- c("SN status",
                                     "Negative SN status",
                                     "Positive SN status", 
                                     "Age", 
                                     "Ulceration",
                                     "Location", 
                                     "Upper limb", 
                                     "Lower limb", 
                                     "Trunk", 
                                     "Head and neck",
                                     "Breslow",
                                     "Breslow (negative)",
                                     "Breslow (positive)",
                                     "SN tumour burden", 
                                   row.names(final.BS.table.Rec.5)[(nrow(final.BS.table.Rec.5)-1):nrow(final.BS.table.Rec.5)])
final.BS.table.MSM.5.refit <- as.data.frame(final.BS.table.MSM.5.refit)
row.names(final.BS.table.MSM.5.refit) <- c("SN status",
                                     "Negative SN status",
                                     "Positive SN status", 
                                     "Age", 
                                     "Ulceration",
                                     "Location", 
                                     "Upper limb", 
                                     "Lower limb", 
                                     "Trunk", 
                                     "Head and neck",
                                     "Breslow",
                                     "Breslow (negative)",
                                     "Breslow (positive)",
                                     "SN tumour burden",  
                                   row.names(final.BS.table.MSM.5.refit)[nrow(final.BS.table.MSM.5.refit)])

@@

CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
utils::write.table(CIndex.Rec.Table,
              file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
              row.names=FALSE, col.names=FALSE, sep=",")

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

# Add C-index to model for Recurrence and MSM refit Table
```{r, eval=TRUE}
for (model in list("Rec.5", "MSM.5.refit")){
  if (model == "Rec.5"){
    # plot predict
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Rec.png"),
        width=1800, height=1800, units="px", res=300)
    plot.predict <- plot(Predict(f.mi.full.Rec.5))
    show(plot.predict)
    grDevices::dev.off()

    # plot predict Breslow
    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/plot.predict.Breslow.Rec.png"),
        width=1800, height=1800, units="px", res=300)
    plot.Breslow <- plot(Predict(f.mi.full.Rec.5, Breslow=0:20, SNstatus), ~ Breslow, groups="SNstatus",
                         adj.subtitle=FALSE, lwd=2, labels=FALSE,
                         par.settings=list(superpose.line=list(lty=c(1, 2), 
                                                               col=c("red", "blue"))),
                         key=list(cex=.8,corner = c(0.1, .9),
                                  lines=list(col=c("red","blue"), 
                                             lty=c(1,2), lwd=2),
                                  text=list(c("Negative","Positive"))))
    show(plot.Breslow)
    grDevices::dev.off()
  }

@@

    # load outcome
    if (model=="Rec.5"){
      S <- S.Rec.training
    }
    else if (model=="MSM.5.refit"){
      S <- S.MSM.training
    }

    png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/all.centers.", model, ".", type, ".png"),
        width=1800, height=1800, units="px", res=300)
    out <- PredictionTools::val.surv.mi(p=p, y=S, g=5, time=5,
                                        main="All centers", CI.metrics=TRUE,
                                        lim=c(0,1), dist=TRUE, n.iter=40)
    grDevices::dev.off()

    final.full.table <- eval(parse(text=paste0("final.", type, ".table.", model)))
    final.full.table["Harrell's C-index", "HR"] <- sprintf("%.2f", out$cindex)
    final.full.table["Harrell's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$cindex.lower),
                                                   "; ", sprintf("%.2f", out$cindex.upper), "]")
    final.full.table["Harrell's optimism-corrected C-index", "HR"] <- sprintf("%.2f", out$cindex-optimism)
    final.full.table["Harrell's optimism-corrected C-index", "CI"] <- paste0("[", sprintf("%.2f", out$cindex.lower-optimism),
                                                   "; ", sprintf("%.2f", out$cindex.upper-optimism), "]")
    final.full.table["Uno's C-index", "HR"] <- sprintf("%.2f", out$unoC)
    final.full.table["Uno's C-index", "CI"] <- paste0("[", sprintf("%.2f", out$unoC.lower),
                                                   "; ", sprintf("%.2f", out$unoC.upper), "]")
    final.full.table["AUC", "HR"] <- sprintf("%.2f", out$AUC)
    final.full.table["AUC", "CI"] <- paste0("[", sprintf("%.2f", out$AUC.lower),
                                                   "; ", sprintf("%.2f", out$AUC.upper), "]")

@@

# Add the C-index for calibrated MSM model to Table for recurrence
```{r, eval=TRUE}
for (type in c("full", "BS")){
  f.mi <- eval(parse(text=paste0("f.mi.", type, ".Rec.5")))
  cindex.MSM <- rep(0, m)
  cindex.se.MSM <- rep(0, m)
  unoC.MSM <- rep(0, m)
  AUC.MSM <- rep(0, m)
  for (i in 1:m){
    lp.i <- predict(f.mi, newdata=mice::complete(imputed.training.data,i), type="lp")

    # Harrell's C-index
    rc <- Hmisc::rcorr.cens(-lp.i, 
                            S.MSM.5.training)
    cindex.MSM[i] <- rc["C Index"]
    cindex.se.MSM[i] <- rc["S.D."]/2

    # Uno's C-index
    Uno.data <- cbind(S.MSM.5.training[, 1], S.MSM.5.training[, 2], lp.i)
    unoC.MSM[i] <- survC1::Est.Cval(mydata=Uno.data, 
                                    tau=horizon, nofit=TRUE)$Dhat
    if (i == 1){
      unoC.boot <- c()
      nr.iter <- 40
      for (itr in 1:nr.iter){
        boot <- Uno.data[sample(1:nrow(Uno.data), nrow(Uno.data), replace=TRUE),]
        unoC <- survC1::Est.Cval(mydata=boot,
                                  tau=horizon,
                                  nofit=TRUE)$Dhat
        unoC.boot <- c(unoC.boot, unoC)
      }
      unoC.MSM.se <- PredictionTools::Rubin.combine(mean(unoC.boot), sd(unoC.boot))$se
    }

    # time-dependent ROC
    AUC.MSM.i <- timeROC::timeROC(T=S.MSM.training[, 1],
                                   delta=S.MSM.training[, 2],
                                   marker=lp.i,
                                   times=horizon,
                                   cause=1, 
                                   iid=FALSE)

    # time-dependent ROC SE
    if (i == 1){
      AUC.MSM.i <- timeROC::timeROC(T=S.MSM.training[, 1],
                                   delta=S.MSM.training[, 2],
                                   marker=lp.i,
                                   times=horizon,
                                   cause=1, 
                                   iid=TRUE)
      AUC.MSM.CI <- stats::confint(AUC.MSM.i)
      AUC.MSM.se <- as.numeric((as.numeric(AUC.MSM.CI$CI_AUC[2])/100-as.numeric(AUC.MSM.i$AUC[2]))/AUC.MSM.CI$C.alpha)
    }
    AUC.MSM[i] <- as.numeric(AUC.MSM.i$AUC[2])
  }
  cindex.mi.MSM <- Rubin.combine(cindex.MSM, cindex.se.MSM)

  final.full.table <- eval(parse(text=paste0("final.", type, ".table.Rec.5")))
  final.full.table["Harrell's C-index MSM", "HR"] <- sprintf("%.2f", cindex.mi.MSM$est)
  final.full.table["Harrell's C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", cindex.mi.MSM$est+qnorm(.025)*cindex.mi.MSM$se),
    "; ", sprintf("%.2f", cindex.mi.MSM$est+qnorm(.975)*cindex.mi.MSM$se), "]")
  final.full.table["Harrell's optimism-corrected C-index MSM", "HR"] <- sprintf("%.2f", cindex.mi.MSM$est-optimism)
  final.full.table["Harrell's optimism-corrected C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", cindex.mi.MSM$est+qnorm(.025)*cindex.mi.MSM$se-optimism),
    "; ", sprintf("%.2f", cindex.mi.MSM$est+qnorm(.975)*cindex.mi.MSM$se-optimism), "]")
  final.full.table["Uno's C-index MSM", "HR"] <- sprintf("%.2f", mean(unoC.MSM))
  final.full.table["Uno's C-index MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", mean(unoC.MSM)+qnorm(.025)*unoC.MSM.se),
    "; ", sprintf("%.2f", mean(unoC.MSM)+qnorm(.975)*unoC.MSM.se), "]")
  final.full.table["AUC MSM", "HR"] <- sprintf("%.2f", mean(AUC.MSM))
  final.full.table["AUC MSM", "CI"] <- paste0("[", 
    sprintf("%.2f", mean(AUC.MSM)+qnorm(.025)*AUC.MSM.se),
    "; ", sprintf("%.2f", mean(AUC.MSM)+qnorm(.975)*AUC.MSM.se), "]")

@@

# set rownames
final.full.table.Rec.5 <- as.data.frame(final.full.table.Rec.5)
row.names(final.full.table.Rec.5) <- c("Positive SN status", "Male",
                                    "Age iqr", "Ulceration", "Location",
                                    "Arm", "Leg", "Trunk", "Head and neck",
                                    "Histology", "SSM", "NM", "ALM", "Other",
                                    "Breslow iqr", "Multiple fields", 
                                    "Total number of negative nodes",
                                    "Total number of positive nodes",
                                    "SN tumour burden iqr", 
                                    "Location metastasis in lymph node",
                                    "Subcap", "Combined", "Parenchymal",
                                    "Multifocal", "Extensive",
                                    rownames(final.full.table.Rec.5)[(nrow(final.full.table.Rec.5)-7):nrow(final.full.table.Rec.5)])
final.full.table.MSM.5.refit <- as.data.frame(final.full.table.MSM.5.refit)
row.names(final.full.table.MSM.5.refit) <- c("Positive SN status", "Male",
                                          "Age", "Ulceration", "Location",
                                          "Arm", "Leg", "Trunk", "Head and neck",
                                          "Histology", "SSM", "NM", "ALM", "Other",
                                          "Breslow", "Multiple fields", 
                                          "Total number of negative nodes",
                                          "Total number of positive nodes",
                                          "SN tumour burden", 
                                          "Location metastasis in lymph node",
                                          "Subcap", "Combined", "Parenchymal",
                                          "Multifocal", "Extensive",
                                          row.names(final.full.table.MSM.5.refit)[(nrow(final.full.table.MSM.5.refit)-3):nrow(final.full.table.MSM.5.refit)])
final.BS.table.Rec.5 <- as.data.frame(final.BS.table.Rec.5)
row.names(final.BS.table.Rec.5) <- c("SN status",
                                     "Negative SN status",
                                     "Positive SN status", 
                                     "Age", 
                                     "Ulceration",
                                     "Location", 
                                     "Upper limb", 
                                     "Lower limb", 
                                     "Trunk", 
                                     "Head and neck",
                                     "Breslow",
                                     "Breslow (negative)",
                                     "Breslow (positive)",
                                     "SN tumour burden", 
                                   row.names(final.BS.table.Rec.5)[(nrow(final.BS.table.Rec.5)-7):nrow(final.BS.table.Rec.5)])
final.BS.table.MSM.5.refit <- as.data.frame(final.BS.table.MSM.5.refit)
row.names(final.BS.table.MSM.5.refit) <- c("SN status",
                                     "Negative SN status",
                                     "Positive SN status", 
                                     "Age", 
                                     "Ulceration",
                                     "Location", 
                                     "Upper limb", 
                                     "Lower limb", 
                                     "Trunk", 
                                     "Head and neck",
                                     "Breslow",
                                     "Breslow (negative)",
                                     "Breslow (positive)",
                                     "SN tumour burden",  
                                   row.names(final.BS.table.MSM.5.refit)[(nrow(final.BS.table.MSM.5.refit)-3):nrow(final.BS.table.MSM.5.refit)])

@@

# optimism-corrected
CIndex.Rec.Table <- rbind(CIndex.BS.Rec.5.All, CIndex.BS.Rec.5.Positive, CIndex.BS.Rec.5.Negative)
CIndex.Rec.Table
# utils::write.table(CIndex.Rec.Table,
#               file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/CIndex.train.txt"),
#               row.names=FALSE, col.names=FALSE, sep=",")

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data", "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

### 2024-01-19 Code/07_CreateCrossValidatedCalibrationPlots.Rmd
Final edits

Centers <- sort(as.character(unique(training.data.to.be.imputed$Center)))
Centers.anonimized <- c("A", "B", "C", "D")
cuts <- 5
for (model in c("Rec.5", "MSM.5")){
  if (model == "Rec.5"){
    S.model <- S.Rec.5.training
  }
  if (model == "MSM.5"){
    S.model <- S.MSM.5.training
  }

  for (type in c("full", "BS")){
    for (j in 1:4){
      S.j<-S.model[training.data.to.be.imputed$Center==Centers[j],]
      S.notj<-S.model[training.data.to.be.imputed$Center!=Centers[j],]
      S.Rec.5.notj<-S.Rec.5.training[training.data.to.be.imputed$Center!=Centers[j],]

@@

        # calibration with metrics
        S <- S.j[select.patients,]
        p <- matrix(NA, nrow(S), m)
        for (i in 1:m){
          data.i <- mice::complete(imputed.training.data, i)
          lp.i <- predict(f.mi.Rec.notj,newdata=data.i[training.data.to.be.imputed$Center==Centers[j],], type="lp")

@@

        # omit the observation with predicted probability = 1
        omit <- unique(c(which(p[,1]==1), which(p[,2]==1), which(p[,3]==1), which(p[,4]==1), which(p[,5]==1)))
        if (length(omit)>0){
          cat("Omit:", omit, "\n")
          p <- p[-omit,]
          S <- S[-omit,]
        }

        png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", model, ".", select.value, ".", type, ".", Centers[j], ".png"))
        out <- PredictionTools::val.surv.mi(p, S, g=5, main=paste("Center", Centers.anonimized[j]),
                                            time=NULL,lim=c(0,1),dist=TRUE)
        grDevices::dev.off()
      }
    }
  }
}

>>>>

Centers <- sort(as.character(unique(training.data.to.be.imputed$Center)))
Centers.anonimized <- c("A", "B", "C", "D")
cuts <- 5
for (model in c("Rec.5", "MSM.5")){
  if (model == "Rec.5"){
    S.full <- S.Rec.training
    S.model <- S.Rec.5.training
  }
  if (model == "MSM.5"){
    S.full <- S.MSM.training
    S.model <- S.MSM.5.training
  }

  for (type in c("full", "BS")){
    for (j in 1:4){
      S.j<-S.model[training.data.to.be.imputed$Center==Centers[j],]
      S.full.j<-S.full[training.data.to.be.imputed$Center==Centers[j],]
      S.notj<-S.model[training.data.to.be.imputed$Center!=Centers[j],]
      S.Rec.5.notj<-S.Rec.5.training[training.data.to.be.imputed$Center!=Centers[j],]

@@

        # calibration with metrics
        # S.full <- S.full.j[select.patients,]
        S <- S.full.j[select.patients,]
        p <- matrix(NA, nrow(S), m)
        for (i in 1:m){
          data.i <- mice::complete(imputed.training.data, i)
          lp.i <- predict(f.mi.Rec.notj,newdata=data.i[training.data.to.be.imputed$Center==Centers[j],], type="lp")

@@

        # omit the observation with predicted probability = 1
        # omit <- unique(c(which(p[,1]==1), which(p[,2]==1), which(p[,3]==1), which(p[,4]==1), which(p[,5]==1)))
        # if (length(omit)>0){
        #   cat("Omit:", omit, "\n")
        #   p <- p[-omit,]
        #   S.full <- S.full[-omit,]
        # }

        png(file=paste0("Z:/Project Melanoom/PaperMelanoma/Results/Figures/", model, ".", select.value, ".", type, ".", Centers[j], ".png"),
            width=1800, height=1800, units="px", res=300)
        out <- PredictionTools::val.surv.mi(p, S, g=5, 
                                            main=paste("Center", Centers.anonimized[j]),
                                            time=5, lim=c(0,1), dist=TRUE,
                                            CI.metrics=TRUE, n.iter=40)
        grDevices::dev.off()
      }
    }
  }
}

### 2024-01-19 Code/08_CreateNomogram.Rmd
Final edits

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data",  "last.imputed.training.data.set", 
            "horizon", "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```

>>>>

save(list=c("dd.training", "training.data.to.be.imputed", "m", 
            "imputed.training.data",  "last.imputed.training.data.set", 
            "horizon", 
            "S.Rec.training", "S.MSM.training",
            "S.Rec.5.training", "S.MSM.5.training",
            "f.mi.full.Rec.5", "f.mi.BS.Rec.5", "f.mi.full.MSM.5.refit", 
            "f.mi.BS.MSM.5.refit", "MSM.cal.fact", "c.Breslow", "optimism",
            "form.full.Rec.5", "form.BS.Rec.5", 
            "form.full.MSM.5.refit", "form.BS.MSM.5.refit", 
            "rc.Rec", "int.Rec", "h0.Rec"),
     file="Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata", compress=TRUE)
```
